A Methodology and Implementation of Automated Emissions Harmonization for Use in Integrated Assessment Models

### 2018-02-05 paper.tex
final self revisions

\begin{abstract}
Emissions harmonization refers to the process used to match greenhouse gas (GHG)
and air pollutant results from Integrated Assessment Models (IAMs) against a
common source of historical emissions. To date, harmonization has been performed
separately by individual modeling teams. For the hand-over of emission data for
the Shared Socioeconomic Pathways (SSPs) to climate model groups, a new
automated approach based on commonly agreed upon algorithms was developed. This
work describes the novel methodology for determining such harmonization methods
and an open-source Python software library implementing the methodology. Results
are shown for two example scenarios (with and without climate policy cases)
using the IAM MESSAGE-GLOBIOM that satisfactorily harmonize over 96\% of the
total emissions trajectories while having a negligible effect on key long-term
climate indicators. This new capability enhances the comparability across
different models, increases transparency and robustness of results, and allows
other teams to easily participate in intercomparison exercises by using the
same, openly available harmonization mechanism.
\end{abstract}

@@

\texttt{aneris}, first made available in 2017, is available online at
\url{https://github.com/gidden/aneris} as a free and open-source Python software
library (approximately 2000 lines of code). The \texttt{aneris} software was
developed by the lead author, Matthew J. Gidden, Ph.D., whose contact
information is shown on the title page of this manuscript. Documentation for the
\texttt{aneris} Python package, including software requirements, is available
\href{http://mattgidden.com/aneris/}{online}.

@@

The remainder of this paper describes the methodology and implementation of the
harmonization software \code{aneris} \cite{matthew_gidden_2017_802832}, written
in the Python programming language (detailed documentation available
\href{http://mattgidden.com/aneris/}{online}). Section \ref{sec:meths} provides
a detailed description of the underlying mathematical components of
\code{aneris} as well as the procedural workflow. The results of applying the
automated harmonization mechanism on two example \gls{iam} scenarios, one with
emissions growth and another with emissions mitigation, is presented in Section
\ref{sec:results}. Finally, the general effectiveness and potential future
improvements on the automated methodology is discussed in Section
\ref{sec:future}.

@@

\subsection{Harmonization Methods}

@@

The goals of any harmonization exercise is threefold: aligning model results in
the harmonization year to a common historical data source, faithfully
representing the original \gls{iam}’s internal consistency between the driver
of emissions (e.g. energy use) and emissions, and maintaining critical
parameters from the original scenario design. All harmonization methods achieve
the first goal by design. If the difference between the model base year and
historical values are small, considering the second and third goals leads to a
\code{reduce\_ratio} method that converges prior to the final model year as the
natural best choice. It preserves the ratio of \gls{iam} output and emissions
inventory in the base year while also matching the original model output at some
point in the modeled time period. It furthermore maintains the consistency of
the model's usage of energy technology, volume of agricultural activities, and
abatement options with harmonized emissions trajectory.

However, other concerns may lead to a better-informed choice than using a
blanket \code{reduce\_ratio} method for all emissions trajectories. For example,
emissions from \gls{luluc} are known to have high year-to-year variation, and
therefore historical data may change drastically depending on the base year
considered. In such a situation, a \code{reduce\_ratio} that converges at a year
past the modeled time period is a better choice in order to smooth out
discrepancies between the historical data used to develop model and the new data
source being used for harmonization.

@@

The value of $c_v$ is then tested against a threshold, $\tau_{c_v}$. To
determine this threshold, an analysis of the recent \gls{ceds} and \gls{luc}
historical data has been performed. Figure \ref{fig:cov} shows the distribution
of \gls{luc} $c_v$s and non-\gls{luc} $c_v$s as determined for historical data
aggregated to the model regions of 5 different \glspl{iam} involved in the
\gls{ssp} process: AIM-CGE \cite{fujimori_ssp3:_2017},
IMAGE\cite{van_vuuren_energy_2017}, GCAM4\cite{calvin_ssp4:_2017},
MESSAGE-GLOBIOM\cite{fricko_marker_2017}, and
REMIND-MAGPIE\cite{kriegler_fossil-fueled_2017}, each of which have varying
definitions of native model regions comprising different collections of
countries. Therefore, each data point comprising Figure \ref{fig:cov} represents
a realization of $c_v$ for a single combination of native model region, sector,
and emissions species \footnote{A full listing of all sectors and species is
  presented in the case-study discussion in Section \ref{sec:results}, Table
  \ref{tab:sp}}. A threshold value of $\tau_{c_v} = 20$ has been chosen based on
these observations as it optimally divides the two distributions. Importantly,
tails of the \gls{luc} and non-\gls{luc} overlap, thus there are both false
positives (~7\% of non-\gls{luc} trajectories) and false negatives (~10\% of
\gls{luc} trajectories). However, as any regional definition is model dependent
and thus any regional aggregation is possible an automated detection mechanism
is necessary.

@@

We herein present \code{aneris}' Python implementation, depicted in Figure
\ref{fig:software}, and conceptual, depicted in Figure \ref{fig:workflow}. The
library is composed of a number of utilities as well as three primary
components: the \texttt{HarmonizationDriver}, \texttt{Harmonizer}, and data
processing routines (shown in red, green, and blue, respectively in Figures
\ref{fig:software} and \ref{fig:workflow}).

@@

The \texttt{Harmonizer} is a Python class whose concern is to harmonize model
value trajectories given historical data and possible user method
\textit{overrides}, i.e., non-default methods (described further below). It is
used by the \texttt{HarmonizationDriver}; however it is also available to the
user as a first-class object. The \texttt{Harmonizer} requires that input data
conform to the \code{aneris} calculation data format, which explicitly separates
the emissions species from the sector contributing the emissions (these are
combined in the single \code{Variable} column in the standard \gls{iam}
format). Because the \texttt{Harmonizer} is designed to operate on a single
instance of a model and scenario, the canonical data format includes
\texttt{region}, \texttt{sector}, \texttt{gas}, and \texttt{units} columns
without extraneous meta-data columns for the model and scenario. Once configured
with appropriate input data (model and history) as well as potential method
overrides, the \texttt{Harmonizer}'s \texttt{harmonize()} method can be invoked
which returns a \texttt{pandas.DataFrame} of harmonized data. The object can
additionally be queried directly as to its \texttt{default\_methods()},
\texttt{methods()} (i.e., methods used with overrides), and \texttt{metadata()}
(i.e., methods used with all branching information along each path in the
decision tree).

@@

The full harmonization workflow, outlined in Figure \ref{fig:workflow}, begins
by cleaning input data, which adds (0-valued) model trajectories that exist in
the historical data set but are not provided by the model input and detects any
issues that would cause the harmonization process to fail. The methods used to
harmonize the data are then determined and the harmonization process is
executed. Upon completion of the harmonization process, aggregation of common
analysis regions is performed. A common regional aggregation used in the
\gls{iam} community was defined in the \glspl{rcp}
\cite{vuuren_representative_2011}, shown in Figure \ref{fig:regions}. Finally,
any exogenous trajectories the user provides are added. Exogenous trajectories
are normally provided for unmodeled gases with well-accepted scenario
trajectories, e.g., chlorofluorocarbons provided by the \gls{wmo}
\cite{wmo2014}. Upon completion, the harmonized trajectories and meta data
regarding the harmonization process are returned. A description of all returned
meta data is provided in Table \ref{tab:metadata}.

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth]{MESSAGE_11-5regions_map.pdf}
    \caption[]{
      \label{fig:regions}
      The 5 regions used in the \glspl{rcp} with their 11-region constituents: Asia
      (\gls{cpa}, \gls{sas}, \gls{pas}) [yellows], \gls{lam}
      [magenta], the \gls{mea} and \gls{afr} [greens], the OECD (\gls{nam},
      \gls{weu}, and \gls{pao}) [blues], and the Reforming Economies
      (\gls{eeu} and \gls{fsu}) [reds].  }
  \end{center}
\end{figure}

@@

@@

In order to help identify cases where overrides may be of interest,
harmonization \textit{diagnostics} are provided which analyze the relative
difference between harmonized and unharmonized trajectories at their mid and
end-points. These values are configurable by the user, but defaults of $400$\%
and $200$\%, respectively, are provided based on experiences of the authors'
using \code{aneris} to date.

@@

In order to show a representative cross section of the performance of the
\code{aneris} harmonization procedure, we focus on the harmonization of results
of the \gls{iam} MESSAGE-GLOBIOM \cite{fricko_marker_2017}. Two scenarios from
the \gls{ssp} scenario library\footnote{We refer the reader to the broad
  literature discussing the SSPs, e.g.,
  \cite{vuuren_new_2013,oneill_scenario_2016, oneill_new_2013} for a more in
  depth discussion of the scenario architecture and design.} are presented. The
SSP2 \cite{Riahi2017153,Rao2017346}, or ``middle of the road'', scenario
(referred to as SSP2-Ref) is chosen to be analyzed because MESSAGE-GLOBIOM is
the marker scenario\footnote{The concept of ``marker'' scenarios are used to
  illustrate distinctive scenario types within the SSP scenario framework. See
  \cite{vuuren_new_2013} and \cite{Riahi2017153} for a more lengthy
  description.} for this \gls{ssp}. This SSP2 scenario lies between two
\glspl{rcp}, 6 and 8.5, with a radiative forcing\footnote{Radiative forcing is a
  measurement of the capacity for different emissions species to affect
  tropopausal irradiance and has a relationship to global mean equilibrium
  temperature change. We refer the reader to \cite{IPCCWG1PhysicalStocker2013}
  for a more detailed discussion.} level of approximately 6.5 Wm$^{-2}$. We
additionally present the results for the SSP2-based mitigation scenario leading
to a radiative forcing of 4.5 Wm$^{-2}$ (referred to as SSP2-4.5). The SSP2-45
scenario is chosen because mitigation technologies and policies are enacted
causing a general reduction in pollutants and \glspl{ghg}, including (eventual)
negative \cotwo emissions in some regions and sectors due to carbon capture and
sequestration and afforestation. A scenario in which negative emissions play a
role in mitigation strategies is particularly important because of the
sensitivity of key indicators, such as end-of-century radiative forcing (which
is used to estimate mean global temperature increase), to the timing and
magnitude of net-zero and total negative \cotwo emissions. Therefore, these two
scenarios represent two relative extreme cases in the use of a harmonization
approach and thus provide a case study as to its general applicability. Figure
\ref{fig:kyoto} shows the different trends of Kyoto Gases in each scenarios.

@@

MESSAGE-GLOBIOM includes a representation of 11 distinct regions which can be
mapped directly to the 5-region definition used in the \glspl{rcp}. Historical data is
taken from previously described \gls{luc} and anthropogenic sources, which comprise 10
separate pollutant and \gls{ghg} species and 12 sectors shown in Table \ref{tab:sp}. A
total of 970 distinct trajectories were harmonized for each scenario, and
therefore 1940 trajectories were harmonized in total. \noxx generated from the
Energy sector provides an example of an emissions species and sector in which
all regions were satisfactorily harmonized with the default methods. Figure
\ref{fig:nox} shows the results of harmonization in Asia, and Table
\ref{tab:nox} describes the parameters that underlie the choice of method for
each harmonized trajectory.

@@

Figure \ref{fig:co} presents a case in which the magnitude of a trajectory is
distorted. A large discrepancy ($\sim$300\% relative difference) is observed in
the harmonization year for carbon monoxide (CO) emissions in the industrial
sector specifically for the \gls{sas} and \gls{afr} MESSAGE-GLOBIOM
regions. Furthermore, emissions in both regions see relatively large expansion
or contraction, depending on the scenario; therefore, both regions are
candidates for choosing harmonization method overrides. The default method
chosen in both cases (\code{constant_ratio}) maintains model trends for the
region; however, overall model results are distorted. By applying a
\code{constant_offset} overrides, the regional trends and magnitudes are
maintained. Through the use of harmonization overrides also ameliorates issues
seen in the harmonized global trajectory of industrial CO (Figure \ref{fig:co},
Panel \textbf{c}). Not only does the global trajectory with overrides more
accurately match the original unharmonized model behavior and magnitude of
emissions, but the relative importance of the underlying regional trajectories
is also maintained.

@@

In certain circumstances, the application of the default harmonization methods
can affect not only the magnitude but also the shape of regional
trajectories. Figure \ref{fig:nh3} shows an example case of emissions
trajectories for ammonia (\nht) from the agriculture sector. Again, the
\gls{sas} region shows a large discrepancy in the harmonization year ($>$150\%
in this case). The resulting trajectory harmonized with the default method
(\code{constant_ratio}) provides a large increase after 2080 in the SSP2
reference scenario. Notably, the SSP2-45 scenario is not affected to the same
degree. While this distortion changes the magnitude of the \gls{sas} trajectory,
it largely affects the post-2080 shape of the global trajectory (Figure
\ref{fig:nh3}, Panel \textbf{b}). For example, in the original model result,
\gls{sas} \nht agricultural emissions contribute $\sim$30\% of total global
emissions, whereas in the unharmonized case with default methods, \gls{sas}
comprises $\sim$50\% of global emissions. By using a \code{constant_offset}
method as an override, this distortion is addressed and more accurately reflects
unharmonized results in the \gls{sas} region, the relative importance between
regions, and global results for agricultural ammonia emissions, each of which
contributes to a better harmonization quality for the harmonized \gls{sas}
trajectory. The harmonized emissions using overrides result in a contribution of
$\sim$32\% of total global emissions by the \gls{sas} region which aligns
closely with the unharmonized model results.

@@

This work provides a new direction and framework which the \gls{iam} and climate
communities can build upon in order to reduce the necessity of consistent expert
opinion and increase transparency and reproducibility of harmonization
exercises. Furthermore, it provides an open-source, tested, and documented
software library which can be used and improved upon by these communities. Both
of these are clear steps in a positive direction for future climate and
integrated assessment modeling exercises.

>>>>

\begin{abstract}
Emissions harmonization refers to the process used to match greenhouse gas (GHG)
and air pollutant results from Integrated Assessment Models (IAMs) against a
common source of historical emissions. To date, harmonization has been performed
separately by individual modeling teams. For the hand-over of emission data for
the Shared Socioeconomic Pathways (SSPs) to climate model groups, a new
automated approach based on commonly agreed upon algorithms was developed. This
work describes the novel methodology for determining such harmonization methods
and an open-source Python software library implementing the methodology. A case
study is presented for two example scenarios (with and without climate policy
cases) using the IAM MESSAGE-GLOBIOM that satisfactorily harmonize over 96\% of
the total emissions trajectories while having a negligible effect on key
long-term climate indicators. This new capability enhances the comparability
across different models, increases transparency and robustness of results, and
allows other teams to easily participate in intercomparison exercises by using
the same, openly available harmonization mechanism.
\end{abstract}

@@

\texttt{aneris}, first made available in 2017, is available online at
\url{https://github.com/gidden/aneris} as a free and open-source Python software
library (approximately 2000 lines of code). The \texttt{aneris} software was
developed by the lead author whose contact information is shown on the title
page of this manuscript. Documentation for the \texttt{aneris} Python package,
including software requirements, is available
\href{http://mattgidden.com/aneris/}{online}.

@@

The remainder of this paper describes the methodology and implementation of the
harmonization software \code{aneris} \cite{matthew_gidden_2017_802832}, written
in the Python programming language (detailed documentation is available
\href{http://mattgidden.com/aneris/}{online}). Section \ref{sec:meths} provides
a detailed description of the underlying mathematical components of
\code{aneris} as well as the procedural workflow. A case study of applying the
automated harmonization mechanism on two example \gls{iam} scenarios, one with
emissions growth and another with emissions mitigation, is presented in Section
\ref{sec:results}. Finally, the general effectiveness and potential future
improvements on the automated methodology is discussed in Section
\ref{sec:future}.

@@

The goals of any harmonization exercise is threefold: aligning model results in
the harmonization year to a common historical data source, faithfully
representing the original \gls{iam}’s internal consistency between the driver of
emissions (e.g. energy use) and emissions, and maintaining critical parameters
from the original scenario design. Any harmonization method achieves the first
goal by design. If the difference between the model base year and historical
values are small, considering the second and third goals leads to a method
choice that matches modeled drivers (e.g., a \code{ratio} method discussed in
Section \ref{sec:harm-methods}) and converges prior to the final model year. It
preserves the relationship between \gls{iam} output and emissions inventory in
the base year while also matching the original model output at some point in the
modeled time period. It furthermore maintains the consistency of the model's
usage of energy technology, volume of agricultural activities, and abatement
options with harmonized emissions trajectory.

However, other concerns may lead to a better-informed choice than using a
blanket method for all emissions trajectories. For example, emissions from
\gls{luluc} are known to have high year-to-year variation, and therefore
historical data may change drastically depending on the base year considered. In
such a situation, a method that converges at a year past the modeled time period
is a better choice in order to smooth out discrepancies between the historical
data used to develop model and the new data source being used for harmonization.

\subsection{Harmonization Methods}\label{sec:harm-methods}

@@

@@

The value of $c_v$ is then tested against a threshold, $\tau_{c_v}$. To
determine this threshold, an analysis of the recent \gls{ceds} and \gls{luc}
historical data has been performed. Figure \ref{fig:cov} shows the distribution
of \gls{luc} $c_v$s and non-\gls{luc} $c_v$s as determined for historical data
aggregated to the model regions of 5 different \glspl{iam} involved in the
\gls{ssp} process: AIM-CGE \cite{fujimori_ssp3:_2017},
IMAGE\cite{van_vuuren_energy_2017}, GCAM4\cite{calvin_ssp4:_2017},
MESSAGE-GLOBIOM\cite{fricko_marker_2017}, and
REMIND-MAGPIE\cite{kriegler_fossil-fueled_2017}, each of which have varying
definitions of native model regions comprising different collections of
countries. Therefore, each data point comprising Figure \ref{fig:cov} represents
a realization of $c_v$ for a single combination of native model region, sector,
and emissions species\footnote{A full listing of all sectors and species is
  presented in the case-study discussion in Section \ref{sec:results}, Table
  \ref{tab:sp}}. A threshold value of $\tau_{c_v} = 20$ has been chosen based on
these observations as it optimally divides the two distributions. Importantly,
tails of the \gls{luc} and non-\gls{luc} overlap, thus there are both false
positives (~7\% of non-\gls{luc} trajectories) and false negatives (~10\% of
\gls{luc} trajectories). However, as any regional definition is model dependent
and thus any regional aggregation is possible an automated detection mechanism
is necessary.

@@

We herein present \code{aneris}' Python implementation and conceptual
design.. The library is composed of a number of utilities as well as three
primary components: the \texttt{HarmonizationDriver}, \texttt{Harmonizer}, and
data processing routines shown in red, green, and blue, respectively in Figures
\ref{fig:software} and \ref{fig:workflow}.

@@

The \texttt{Harmonizer} is a class whose concern is to harmonize model value
trajectories given historical data and possible user method \textit{overrides},
i.e., non-default methods (described further in Section \ref{sec:overrides}). It
is used by the \texttt{HarmonizationDriver}; however it is also available to the
user as a first-class object. The \texttt{Harmonizer} requires that input data
conform to the \code{aneris} calculation data format, which explicitly separates
the emissions species from the sector contributing the emissions (these are
combined in the single \code{Variable} column in the standard \gls{iam}
format). Because the \texttt{Harmonizer} is designed to operate on a single
instance of a model and scenario, the canonical data format includes
\texttt{region}, \texttt{sector}, \texttt{gas}, and \texttt{units} columns
without extraneous meta-data columns for the model and scenario. Once configured
with appropriate input data (model and history) as well as potential method
overrides, the \texttt{Harmonizer}'s \texttt{harmonize()} method can be invoked
which returns a \texttt{pandas.DataFrame} of harmonized data. The object can
additionally be queried directly as to its \texttt{default\_methods()},
\texttt{methods()} (i.e., methods used with overrides), and \texttt{metadata()}
(i.e., methods used with all branching information along each path in the
decision tree).

@@

The full harmonization workflow, outlined in Figure \ref{fig:workflow}, begins
by cleaning input data. Cleaning operations include adding (0-valued) model
trajectories that exist in the historical data set but are not provided by the
model input and detecting any issues that would cause the harmonization process
to fail. The methods used to harmonize the data are then determined and the
harmonization process is executed. Upon completion of the harmonization process,
spatial aggregation to common analysis regions is performed. For example, the
5-region aggregation developed in the \glspl{rcp}
\cite{vuuren_representative_2011} process is commonly used in the \gls{iam}
community and is shown in Figure \ref{fig:regions}. Finally, any exogenous
trajectories the user provides are added. Exogenous trajectories are normally
provided for unmodeled gases with well-accepted scenario trajectories, e.g.,
chlorofluorocarbons provided by the \gls{wmo} \cite{wmo2014}. Upon completion,
the harmonized trajectories and meta data regarding the harmonization process
are returned. A description of all returned meta data is provided in Table
\ref{tab:metadata}.

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth]{MESSAGE_11-5regions_map.pdf}
    \caption[]{
      \label{fig:regions}
      The 5 regions used in the \glspl{rcp} with their MESSAGE-GLOBIOM 11-region
      constituents: Asia (\gls{cpa}, \gls{sas}, \gls{pas}) [yellows], \gls{lam}
      [magenta], Africa and the Middle East (\gls{mea} and \gls{afr}) [greens],
      the OECD (\gls{nam}, \gls{weu}, and \gls{pao}) [blues], and the Reforming
      Economies (\gls{eeu} and \gls{fsu}) [reds].  }
  \end{center}
\end{figure}

@@

\subsection{User-Defined Override Methods}\label{sec:overrides}

@@

In order to help identify cases where overrides may be of interest,
harmonization \textit{diagnostics} are provided which analyze the relative
difference between harmonized and unharmonized trajectories at their mid and
end-points. These values are configurable by the user, but defaults of $400$\%
and $200$\%, respectively, are provided based on experiences of the authors'
use of \code{aneris} to date.

@@

In order to show a representative cross section of the performance of the
\code{aneris} harmonization procedure, we focus on the harmonization of results
of the \gls{iam} MESSAGE-GLOBIOM \cite{fricko_marker_2017}. Two scenarios from
the \gls{ssp} scenario library\footnote{We refer the reader to the broad
  literature discussing the SSPs, e.g.,
  \cite{vuuren_new_2013,oneill_scenario_2016, oneill_new_2013} for a more in
  depth discussion of the scenario architecture and design.} are presented. The
SSP2 \cite{Riahi2017153,Rao2017346}, or ``middle of the road'', scenario
(referred to as SSP2-Ref) is chosen to be analyzed because MESSAGE-GLOBIOM is
the marker scenario\footnote{The concept of ``marker'' scenarios are used to
  illustrate distinctive scenario types within the SSP scenario framework. See
  \cite{vuuren_new_2013} and \cite{Riahi2017153} for a more lengthy
  description.} for this \gls{ssp}. This SSP2 scenario lies between two
\glspl{rcp}, 6 and 8.5, with a radiative forcing\footnote{Radiative forcing is a
  measurement of the capacity for different emissions species to affect
  tropopausal irradiance and has a relationship to global mean equilibrium
  temperature change. We refer the reader to \cite{IPCCWG1PhysicalStocker2013}
  for a more detailed discussion.} level of approximately 6.5 Wm$^{-2}$. We
additionally present the results for the SSP2-based mitigation scenario leading
to a radiative forcing of 4.5 Wm$^{-2}$ (referred to as SSP2-4.5). The SSP2-45
scenario is chosen because mitigation technologies and policies are enacted
causing a general reduction in pollutants and \glspl{ghg}, including (eventual)
negative \cotwo emissions in some regions and sectors due to carbon capture and
sequestration and afforestation. A scenario in which negative emissions play a
role in mitigation strategies is particularly important because of the
sensitivity of key indicators, such as end-of-century radiative forcing (which
is used to estimate mean global temperature response), to the timing and
magnitude of net-zero and total negative \cotwo emissions. Therefore, these two
scenarios represent two bounding cases in the use of a harmonization approach
and thus provide a case study as to its general applicability. Figure
\ref{fig:kyoto} shows the different trends of Kyoto Gases, a measure of
aggregate \gls{ghg} emissions, in each scenarios.

@@

MESSAGE-GLOBIOM includes a representation of 11 distinct regions which can be
mapped directly to the 5-region definition used in the \glspl{rcp}. Historical
data is taken from previously described \gls{luc} and anthropogenic sources,
which comprise 10 separate pollutant and \gls{ghg} species and 12 sectors shown
in Table \ref{tab:sp}. A total of 970 distinct trajectories were harmonized for
each scenario, and therefore 1940 trajectories were harmonized in total. \noxx
generated from the Energy sector provides an example of an emissions species and
sector in which all regions were satisfactorily harmonized with the default
methods. Figure \ref{fig:nox} shows the results of harmonization in Asia, and
Table \ref{tab:nox} describes the parameters that underlie the choice of method
for each harmonized trajectory. Importantly, the default methods provide
regional trajectories for both the reference and mitigation scenarios closely
matching the unharmonized model behavior and also result in global aggregates
that agree with the unharmonized trajectory over the modeled time period.

@@

Figure \ref{fig:co} presents a case in which the magnitude of a trajectory is
distorted. A large discrepancy ($\sim$300\% relative difference) is observed in
the harmonization year for carbon monoxide (CO) emissions in the industrial
sector specifically for the \gls{sas} and \gls{afr} regions. Furthermore,
emissions in both regions see relatively large expansion or contraction,
depending on the scenario; therefore, both regions are candidates for choosing
harmonization method overrides. The default method chosen in both cases
(\code{constant_ratio}) maintains model trends for the region; however, overall
model results are distorted as can be seen in both the regional and global
panels in Figure \ref{fig:co}. By applying \code{constant_offset} overrides, the
regional trends and magnitudes are maintained. The use of harmonization
overrides also ameliorates issues seen in the harmonized global trajectory of
industrial CO (Figure \ref{fig:co}, Panel \textbf{c}). Not only does the global
trajectory with overrides more accurately match the original unharmonized model
behavior and magnitude of emissions, but the relative importance of the
underlying regional trajectories is also maintained.

@@

In certain circumstances, the application of the default harmonization methods
can affect not only the magnitude but also the shape of regional
trajectories. Figure \ref{fig:nh3} shows an example case of emissions
trajectories for ammonia (\nht) from the agriculture sector. Again, the
\gls{sas} region shows a large discrepancy in the harmonization year ($>$150\%
in this case). The resulting trajectory harmonized with the default method
(\code{constant_ratio}) provides a large increase after 2080 in the SSP2
reference scenario. Notably, the SSP2-45 scenario is not affected to the same
degree. While this distortion changes the magnitude of the \gls{sas} trajectory,
it largely affects the post-2080 shape of the global trajectory (Figure
\ref{fig:nh3}, Panel \textbf{b}) as well as the relative regional contributions
to the global aggregate trajectory. For example, in the original model result,
\gls{sas} \nht~ agricultural emissions contribute $\sim$30\% of total global
emissions, whereas in the unharmonized case with default methods, \gls{sas}
comprises $\sim$50\% of global emissions by 2100. By using a
\code{constant_offset} method as an override, this distortion is addressed and
more accurately reflects unharmonized results in the \gls{sas} region, the
relative importance between regions, and global results for agricultural ammonia
emissions, each of which contributes to a better harmonization quality for the
harmonized \gls{sas} trajectory. The harmonized emissions using overrides result
in a contribution of $\sim$32\% of total global emissions by the \gls{sas}
region which aligns closely with the unharmonized model results.

@@

This work provides a new direction and framework which the \gls{iam} and climate
science communities can build upon in order to reduce the necessity of
consistent expert opinion and increase transparency and reproducibility of
harmonization exercises. Furthermore, it provides an open-source, tested, and
documented software library which can be used and improved upon by these
communities. Both of these are clear steps in a positive direction for future
climate and integrated assessment modeling exercises.
